Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-20 bdcloud_paper/latex/paper.tex
Highlighted abstract / keywords
Added keywords
edits to intro

\begin{abstract}
%\boldmath
Abstract
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

@@

Several synethic data set generators exist.  TeraGen \textcolor{red}{cite} and the Intel Hadoop Benchmark Suite \cite{Huang2010} can generate data sets quickly and at any scale. Targetted towards specific benchmarks such as Map-Reduce jobs and Hive queries, the resulting data is semantically-void and not useful for other tasks.  Multiple frameworks exist for generating synthetic data sets that satisfy relational database schemas \cite{Ghazal2013,Rabl2011a,Frank2012,Rabl2011,Gray1994,Bruno2005}. The more advanced approaches of these allow users to specify relationships between field values through simple arithmetic equations for setting the value of fields from other fields \cite{Alexandrov2012} or use constraint-solving techniques \cite{Arasu2011}. However, due to the inability to specify underlying dynamic models with latent variables, the generated data lacks informational complexity and genuine semantics, making it inapprioriate for analytics.

Recent work is focused on generating synthetic data sets that satisfy characteristics learned from a real reference data sets \cite{Alexandrov2013}. Such approaches appear promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models that capture the effect of latent variables.

>>>>

\begin{abstract}
%\boldmath
\textcolor{red}{Abstract}

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\begin{IEEEkeywords}
big data, synthetic, data set, data generation, benchmarking, testing, probabilistic models
\end{IEEEkeywords}

@@

Several synethic data set generators exist.  TeraGen \textcolor{red}{cite} and the Intel Hadoop Benchmark Suite \cite{Huang2010} can generate data sets quickly and at any scale. Targetted towards specific benchmarks such as Map-Reduce jobs and Hive queries, the resulting data is semantically-void and not useful for other tasks.  Multiple frameworks exist for generating synthetic data sets that satisfy relational database schemas \cite{Ghazal2013,Rabl2011a,Frank2012,Rabl2011,Gray1994,Bruno2005,Hoag2007}. Several approaches use domain-specific langugages \cite{Bruno2005,Hoag2007} to allow users to specify additional constraints such as which distributions to sample from or allow modeling basic relationships between fields such as simple arithmetic equations \cite{Alexandrov2012}. Arasu, et al. \cite{Arasu2011} demonstrated how constraint-solving techniques could be used as an alternative to procedural approaches. These frameworks allow for reproducing the structural properties of real data, but the frameworks are not expressive enough to describe the dynamic generation processes and latent variables that would be needed to embed the desired informational complexity and rich semantics needed for analytics.

Realizing the difficulty in creating a generic framework capable of modeling the semantics of deep domain knowledge, recent work\cite{Alexandrov2013} has focused on generating synthetic data sets that satisfy characteristics learned from a real reference data sets. Such approaches appear promising but will need to overcome the difficulties of accurately training models, especially on raw data instead of features.
